---
title: "Climate Congressional Record and Climate Hansard Topic Modelling"
output: pdf_document
fontsize: 12pt
---

This R markdown document contains the code to create a topic model of the Climate Congressional Record and Climate Hansard datasets. A topic model is used to investigate the following hypotheses:

- H3: Between 1997 and 2015, there was a stronger association between party affiliation and pro- or anti-environmental topic prevalence among US legislators’ climate policy speeches than among UK legislators’ speeches. 

- H4: Between 1997 and 2015, the words used in US legislators’ climate policy speeches exhibited more variation between elections and non-electoral periods than in UK speeches. 

- H5: During this period, the association between pro- or anti-environmental topic prevalence and public opinion was stronger in US legislators’ climate policy speeches than in UK speeches. 

# Setup

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(janitor)
library(stringr)
library(quanteda)
library(stm)

DATA_PATH <- "data/"
DIST_PATH <- "dist/"

NUM_TOPICS <- 18

climate_congressional_record <-
    read_csv(paste0(DATA_PATH, "climate_congressional_record.csv"))
climate_hansard <-
    read_csv(paste0(DATA_PATH, "climate_hansard.csv"))

election_dates <-
    read_csv(paste0(DATA_PATH, "election_dates_1997_2015.csv")) |>
    clean_names() |>
    mutate(
        date = as.character(date) |> as.Date(date, format = "%B %d, %Y")
    )

ELECTION_PERIOD_DAYS <- 42
```

# Data Preprocessing

## Cleaning the Climate Congressional Record dataset

```{r}
partitioned_climate_congressional_record <- climate_congressional_record |>
    rename(
        family_name = last_name,
        speech_date = date,
        speech_party = party,
        text = speech
    ) |>
    mutate(
        across(c(first_name, family_name), str_to_title),
        name = paste(first_name, family_name, sep = " ") |> str_to_title(),
        speech_party = case_when(
            speech_party == "R" ~ "Republican",
            speech_party == "D" ~ "Democrat",
            TRUE ~ "Other"
        ),
        speech_id = as.character(speech_id),
        chamber = case_when(
            chamber == "H" ~ "House",
            chamber == "S" ~ "Senate"
        )
    ) |>
    select(
        speech_id,
        name,
        first_name,
        family_name,
        speech_date,
        speech_party,
        text,
        cleaned_stems,
        chamber
    ) |>
    mutate(country = "USA")
```

## Cleaning the Climate Hansard dataset

```{r}
partitioned_climate_hansard <- climate_hansard |>
    select(
        speech_id,
        name,
        first_name,
        family_name,
        speech_date,
        speech_party,
        text,
        cleaned_stems
    ) |>
    filter(!is.na(speech_party)) |>
    mutate(
        speech_party = case_when(
            speech_party == "Labour/Co-operative" ~ "Labour",
            TRUE ~ speech_party
        ),
        chamber = "House of Commons",
        country = "UK"
    ) |>
    mutate(
        speech_party = if_else(speech_party %in% c("Conservative", "Labour"),
            speech_party,
            "Other"
        )
    )
```

## Combining the Climate Congressional Record and Climate Hansard datasets

```{r}
complete_climate_speeches <- bind_rows(
    partitioned_climate_congressional_record,
    partitioned_climate_hansard
) |>
    arrange(speech_date) |>
    mutate(
        date_as_numeric = as.numeric(speech_date),
        affiliation = case_when(
            speech_party %in% c("Democrat", "Labour") ~ "Left",
            speech_party %in% c(
                "Republican", "Conservative"
            ) ~ "Right",
            TRUE ~ "Neutral"
        )
    )
```

### Recording if a speech was made within 6 weeks of an election

```{r}
in_election_period <- function(row) {
    speech_date <- row$speech_date
    chamber <- row$chamber

    if (chamber == "House" | chamber == "Senate") {
        house_election_dates <- election_dates |>
            filter(election_type == "US Congressional") |>
            pull(date)
        return(
            any(abs(house_election_dates - speech_date) <= ELECTION_PERIOD_DAYS)
        )
    } else if (chamber == "House of Commons") {
        uk_election_dates <- election_dates |>
            filter(election_type == "UK General") |>
            pull(date)
        return(
            any(abs(uk_election_dates - speech_date) <= ELECTION_PERIOD_DAYS)
        )
    }
}

complete_climate_speeches <- complete_climate_speeches |>
    mutate(
        in_election_period = map_lgl(
            seq_len(nrow(complete_climate_speeches)),
            ~ in_election_period(complete_climate_speeches[.x, ])
        )
    )
```

## Creating a Climate Speeches DFM

```{r}
climate_speeches_corpus <-
    corpus(
        complete_climate_speeches,
        text_field = "cleaned_stems"
    )
climate_speeches_dfm <-
    climate_speeches_corpus |>
    tokens() |>
    dfm()
```

# Testing Hypothesis 3

## Fitting a structural topic model with an interaction between `affiliation` and `county`, and `date_as_numeric` added as a covariate

```{r}
party_interaction_stm <- stm(
    documents = climate_speeches_dfm,
    prevalence = ~ affiliation * country + s(date_as_numeric),
    K = NUM_TOPICS,
    seed = 42
)
save(party_interaction_stm, file = paste0(
    DATA_PATH,
    "party_interaction_stm.RData"
))
load(paste0(DATA_PATH, "party_interaction_stm.RData"))
```

## Investigating the model's topics

```{r}
labelTopics(party_interaction_stm)
findThoughts(party_interaction_stm,
    texts = climate_speeches_dfm$text,
    n = 2
)
plot.STM(party_interaction_stm,
    type = "summary",
    labeltype = "score"
)

score_topic_labels <- labelTopics(party_interaction_stm)$score
topic_labels <-
    apply(score_topic_labels, 1, function(x) paste(x, collapse = "_"))
```

## Testing Hypothesis 3

### Estimating the effect of `affiliation`, `country`, and their interaction on topic prevalence and adding a covariate for `date_as_numeric`

```{r}
party_prevalence_effects <- estimateEffect(
    formula =
        c(seq_len(NUM_TOPICS)) ~ affiliation * country + s(date_as_numeric),
    stmobj = party_interaction_stm,
    metadata = docvars(climate_speeches_dfm),
    uncertainty = "None"
)
summary(party_prevalence_effects)
```

### Visualising how topic prevalance varies by party affiliation

```{r}
par(mar = c(3, 5, 3, 5), oma = c(0, 5, 2, 0))
layout(matrix(seq_len(NUM_TOPICS), ncol = 2, byrow = TRUE))
for (i in seq_len(NUM_TOPICS)) {
    plot.estimateEffect(
        party_prevalence_effects,
        type = "labels",
        covariate = "affiliation",
        topics = i,
        method = "pointestimate",
        xlab = "Topic Prevalence",
        main = paste0("Topic ", i, ": ", topic_labels[i])
    )
}
title("Topic Prevalence by Affiliation", outer = TRUE)
layout(1)
par(mar = c(5.1, 4.1, 4.1, 2.1), oma = c(0, 0, 0, 0))
```

# Testing Hypothesis 4

## Fititng a US and a UK structural topic model, allowing vocabulary to vary by `in_election_period`

### US STM

```{r}
us_election_period_stm <- stm(
    documents = dfm_subset(
        climate_speeches_dfm, country == "USA"
    ),
    content = ~in_election_period,
    K = NUM_TOPICS,
    seed = 42
)
save(us_election_period_stm, file = paste0(
    DATA_PATH,
    "us_election_period_stm.RData"
))
load(paste0(DATA_PATH, "us_election_period_stm.RData"))
```

### Investigating the US model's topics

```{r}
labelTopics(us_election_period_stm)
findThoughts(us_election_period_stm,
    texts = dfm_subset(climate_speeches_dfm, country == "USA")$text,
    n = 2
)
plot.STM(us_election_period_stm,
    type = "summary"
)

us_topics_topic_labels <- labelTopics(us_election_period_stm)$topics
us_topic_labels <-
    apply(us_topics_topic_labels, 1, function(x) paste(x, collapse = "_"))
```

### UK STM

```{r}
uk_election_period_stm <- stm(
    documents = dfm_subset(
        climate_speeches_dfm, country == "UK"
    ),
    content = ~in_election_period,
    K = NUM_TOPICS,
    seed = 42
)
save(uk_election_period_stm, file = paste0(
    DATA_PATH,
    "uk_election_period_stm.RData"
))
load(paste0(DATA_PATH, "uk_election_period_stm.RData"))
```

### Investigating the UK model's topics

```{r}
labelTopics(uk_election_period_stm)
findThoughts(uk_election_period_stm,
    texts = dfm_subset(climate_speeches_dfm, country == "UK")$text,
    n = 2
)
plot.STM(uk_election_period_stm,
    type = "summary"
)

uk_topics_topic_labels <- labelTopics(uk_election_period_stm)$topics
uk_topic_labels <-
    apply(uk_topics_topic_labels, 1, function(x) paste(x, collapse = "_"))
```

## Visualising how vocabulary varies by `in_election_period`

### US STM

```{r}
par(mar = c(3, 5, 3, 5), oma = c(0, 5, 2, 0))
layout(matrix(seq_len(NUM_TOPICS), ncol = 2, byrow = TRUE))
for (i in seq_len(NUM_TOPICS)) {
    plot.STM(us_election_period_stm,
        type = "perspectives",
        topics = i,
        main = paste0("US Topic ", i, ": ", us_topic_labels[i])
    )
}
```

### UK STM

```{r}
par(mar = c(3, 5, 3, 5), oma = c(0, 5, 2, 0))
layout(matrix(seq_len(NUM_TOPICS), ncol = 2, byrow = TRUE))
for (i in seq_len(NUM_TOPICS)) {
    plot.STM(uk_election_period_stm,
        type = "perspectives",
        topics = i,
        main = paste0("UK Topic ", i, ": ", uk_topic_labels[i])
    )
}
```
